% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Victoria C. Wu}
% \address used twice to have two lines of address
\address{\hfill 11408 Colorado Ave \#12, Kansas City, MO 64137}
\address{\hfill (913)235-1070 \textbar \textbar  victoria.chen.wu@gmail.com}

 
\begin{resume}
 
\section{OBJECTIVE}       A position in the field of computers with special 
                interests in business applications programming, 
                information processing, and management systems. 
 
 
\section{EDUCATION} {\sl Bachelor of Science,} Computer Science\\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                University of Missouri - Kansas City, Kansas City, MO \\
                expected December 2014 

\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} 
		C++, Python, Java \\
		ROS, Arduino \\
                {\sl Operating Systems:} Windows, Linux 
 
\section{EXPERIENCE} 
		{\sl Undergrad Research Assistant} \hfill Fall 2013 - Current \\
                ???? 
                Financial Planning Department, Latham, NY
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developed four "user friendly" forecasting 
                    systems each of which produces 18 to 139 
                    individual reports. 
                \item   Developed or improved almost all IFPS 
                    programs used for financial reports. 
                \end{itemize}
 

		{\sl Business Applications Programmer} \hfill Fall 1990 \\
                Allied-Signal Bendix Friction Materials Division, 
                Financial Planning Department, Latham, NY
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developed four "user friendly" forecasting 
                    systems each of which produces 18 to 139 
                    individual reports. 
                \item   Developed or improved almost all IFPS 
                    programs used for financial reports. 
                \end{itemize}
 
                {\sl Research Programmer} \hfill            Summer 1990 \\
                Psychology Department, Rensselaer Polytechnic 
                Institute 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Performed computer aided statistical analysis 
                    of data. 
                 \end{itemize} 
                {\sl Assistant Manager} \hfill        Summers 1988-89 \\
                Thunder Restaurant, Canton, CT
                  \begin{itemize}
                   \item Recognized need for, developed, and wrote 
                    employee training manual. Performed various 
                    duties including cooking, employee training, 
                    ordering, and inventory control. 
                   \end{itemize} 
 
\section{COMMUNITY \\ SERVICE}  
                FIRST Tech Challenge Qualications, Scorekeeper \hfill Feb 2013 \\
		FIRST LEGO League Qualifications, Robot Design Judge \hfill Dec 2012 
	
\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
		Chair, ACM Student Chapter \hfill Fall 2013 - Current \\
            	CS Tutor, UPE \hfill Fall 2013 - Current \\
		Secretary, ACM Student Chapter \hfill Fall 2012 - Spring 2013 \\	
		Secretary, UMKC Robotics Team \hfill  Fall 2012 - Spring 2013 \\	
		Peer Mentor, UMKC School of Computing and Engineering \hfill Fall 2012 - Spring 2013 \\	
		Programmer, UMKC Robotics Team \hfill Spring 2012 - Current \\
		Member, ACM Student Chapter \hfill Fall 2011 - Current 

\end{resume}
\end{document}







